---
title       : Coffee Shop Clusters in Soho, London
subtitle    : Clustering coffee shops by popularity and proximity to Oxford Circus
author      : Darren Wilkinson
job         : 
framework   : io2012     # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : bootstrap    # {mathjax, quiz, bootstrap}
revealjs    : {theme: solarized}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
<style>
.title-slide {
  background-color: #ff6600; /* #EDE0CF; ; #CA9F9D*/
}

.title-slide hgroup > h1{
 font-family: 'Calibri', 'Helvetica', sanserif; 
}

</style>

## Introduction


1. The objective is to group coffee shops in Soho, London so that users can make the most informed choices of where to go based on proximity and popularity metrics.

2. The data can also be used to derive strategies for market positioning in a very competitive market.

3. The clustering tool allows k-means clustering analysis to derive target sub-groups using pairwise mixes of parameters. 

4. The parameters are derived from distance measures, ratings and the number of reviews.

https://wilkinsondi.shinyapps.io/ShinyApp


--- .class #id 

## Data
```{r, echo=FALSE, message=FALSE}
#Generate dataset
names <- c("FlatWhite","TapCoffee","FW","Yumchaa","Foxcroft","Princi","Sacred","SohoGrind",
           "SohoJoe","Algeria","Tapped","Tonic")
reviews <- c(131,28,30,117,77,215,59,16,38,41,8,5)
ratings <- c(4,4,4.5,4,4,4,4,4,4,4.5,4,4)
popularity <- sqrt(reviews)*ratings
placelat <- c(51.513634,51.5154582,51.5129769,51.5152026,51.5129414,51.513846,51.5129446,51.5121446,51.5142755,51.5129833,51.5154582,51.5108185)
placelon <- c(-0.1347613,-0.1358109,-.1364166,-.1361384,-.1341842,-.134522,-.138911,-.1383674,-.1326885,-.1322946,-.1358109,-.1357307)
points <- cbind(placelon,placelat)
rankpop <- as.numeric(rank(-popularity,na.last=TRUE))
lonox <- c(-0.141921) #Calc of distances from Oxford Circus
lonoxdist <- abs(placelon-lonox) #Calc of distances from Oxford Circus
latox <- c(51.515006)
latoxdist <- abs(placelat-latox)
distfactor <- lonoxdist+latoxdist
rankdist <- as.numeric(rank(distfactor,na.last=TRUE))
df <- as.data.frame(c(1:12)) # Add into data frame
names(df)[1] <-"site"
df <- cbind(df, names,reviews,ratings,popularity,placelat,placelon,rankpop,distfactor,rankdist)
df2 <- subset(df,select=c(popularity,distfactor,reviews,rankpop,rankdist))
df3 <- subset(df,select=c(names,popularity,distfactor,reviews,rankpop,rankdist))
datac <- subset(df,select=c(rankdist,rankpop))
```

- Data is from Google and Yelp for 12 coffee shops (16Nov15).
- Popularity = rating score / sqrt(number of reviews)
- Distance = coffee shop (lat,lon) minus Oxford Circus (lat,lon).
```{r, echo=FALSE}
df3
```

---.class #id

## Locations
```{r}
plot(placelon, placelat) # Co-ordinates of coffee shops
```

---bg:#ff6600

## Outcomes
- A k-means clustering analysis is used to analyse target sub-groups.
- The distance rank and popularity rank with k-means of 3 yields a clear clustering for coffee shop segmentation for the discerning coffee drinker or coffee shop strategist. 
    - This is a crude prototype model that can be evolved in many ways.
    - Include more coffee shops over a wider area
    - More sophisticated distance parameters
    - More features to differentiate offerings
    - More sophisticated model
    - Better integration of analytics and mapping tools


```{r, echo=FALSE,message=FALSE, eval=FALSE}
require(cluster)
require(fpc)
clusters <- kmeans(datac, 3)
plot(rankdist,rankpop, col = clusters$cluster, pch = 20, cex = 3)
points(clusters$centers, pch = 3, cex = 4, lwd = 3)

```







